---
title: "FPRO Markdown"
author: "Lib"
date: "04/08/2020"
output: html_document
---
```{r setup, include=FALSE}
#.libPaths("C:Program Files/R/R-3.5/library")
#devtools::install_github("crsh/papaja")
library(Matrix)
library(lme4)
library(lmerTest)
library(emmeans)
library(stats)
library(fitdistrplus)
library(tidyverse)
library(buildmer)
library(performance)
library(see)
```


```{r analysis preferences}
#Set seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Research Questions

As readers do we predict upcoming information before it is encountered in order to better understand the unfolding discourse? 

If prediction is not utilized do we rely on more on basic integration to understand an unfolding discourse context?

Do individual differences contribute to our ability to predict and/or integrate upcoming information? How do these contribute? 

```{r import-and-merge-data, echo=FALSE, message=FALSE}
library(readr)
FPRO_ED_batch_corr <- read_csv("FPRO_ED_batch_corr.csv")
FPRO_ED_batch_error <- read_csv("FPRO_ED_batch_error.csv")
#Rename the participant numbers in the batches back to their oFPROginal participant numbers.
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 54] <-"84"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 53] <-"83"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 52] <-"82"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 51] <-"81"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 50] <-"80"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 49] <-"79"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 48] <-"78"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 47] <-"77"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 46] <-"76"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 45] <-"75"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 44] <-"74"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 43] <-"73"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 42] <-"72"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 41] <-"71"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 40] <-"70"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 39] <-"69"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 38] <-"68"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 37] <-"67"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 36] <-"66"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 35] <-"64"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 34] <-"62"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 33] <-"60"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 32] <-"58"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 31] <-"56"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 30] <-"54"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 29] <-"52"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 28] <-"50"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 27] <-"48"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 26] <-"46"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 25] <-"44"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 24] <-"43"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 23] <-"42"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 22] <-"40"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 21] <-"39"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 20] <-"38"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 19] <-"36"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 18] <-"35"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 17] <-"34"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 16] <-"32"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 15] <-"30"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 14] <-"28"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 13] <-"26"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 12] <-"24"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 11] <-"22"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 10] <-"20"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 9] <-"18"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 8] <-"16"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 7] <-"14"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 6] <-"12"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 5] <-"10"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 4] <-"8"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 3] <-"6"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 2] <-"4"
FPRO_ED_batch_corr$subj[FPRO_ED_batch_corr$subj == 1] <-"2"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 31] <-"65"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 30] <-"63"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 29] <-"61"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 28] <-"59"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 27] <-"57"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 26] <-"55"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 25] <-"53"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 24] <-"51"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 23] <-"49"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 22] <-"47"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 21] <-"45"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 20] <-"41"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 19] <-"37"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 18] <-"35"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 17] <-"33"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 16] <-"31"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 15] <-"29"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 14] <-"27"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 13] <-"25"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 12] <-"23"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 11] <-"21"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 10] <-"19"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 9] <-"17"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 8] <-"15"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 7] <-"13"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 6] <-"11"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 5] <-"9"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 4] <-"7"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 3] <-"5"
FPRO_ED_batch_error$subj[FPRO_ED_batch_error$subj == 2] <-"3"

#Check the subject numbers have been redefined correctly
#View(FPRO_ED_batch_corr)
#View(FPRO_ED_batch_error)

#Let's combine the data
all_data <- rbind(FPRO_ED_batch_corr, FPRO_ED_batch_error)

#make subj a factor
all_data$subj <- as.factor(all_data$subj)

#Import Individual difference measures
All_IDs <- read_csv("../../All_IDs.csv")
#View(All_IDs)

# Rename Participabt in ID_measures to subj to be the same as current data set
All_IDs <- rename(All_IDs, subj = Participant)
All_IDs$subj <- as.factor(All_IDs$subj)

# Add the ID's to the data frame
all_data_join <- inner_join(all_data, All_IDs, by = "subj")
#view(all_data_join)

# Assign condition labels, 1 = prediction facilitated, 2 = prediction unfacilitated
#(this will make it easier to interpret)
all_data_join$cond <- recode(all_data_join$cond, "1" = "facilitated", "2" = "unfacilitated")

```

# Region 4: The question
Let's have a look at various models for our critical region of interest, the question.

```{r Setup-R4}
#Let's have a look at region 4

#set condition as a factor
all_data_join$cond <- as.factor(all_data_join$cond)
```

## Eye-tracking only model
```{r summary-visuals-eyetrackingonly-R4}
#Let's have a look at region 4

all_data_join$R4[all_data_join$R4 == 1] <-"100"
all_data_join$R4 <- as.factor(all_data_join$R4)

#Visualisation
all_data_join %>% 
  ggplot(aes(x = cond, y = R4, colour = cond)) + ggtitle("Regressions In for Critical Region: Question") +
  labs(y = "Regression", x = "Prediction") +
  geom_violin() +
  geom_jitter(alpha = .2, width = .1) +
  stat_summary(fun.data = "mean_cl_boot", colour = "black") +
  guides(colour = FALSE)

```

```{r summary-stats-eyetrackingonly-R4}
# Model assuming normality of residuals maximal structure
#model.nullR4 <- lmer(R4 ~ (1 + cond | subj) + (1 + cond | item), all_data_join) 
modelR4 <- glmer(R4 ~ cond + (1 | subj) + (1 | item), all_data_join, family = "binomial") 
summary(modelR4)

#anova(modelR4, model.nullR4)

#All the data for this model looks pretty normal.
check_model(modelR4)
#qqnorm(residuals(modelR4))
#qqline(residuals(modelR4))
#descdist(all_data_join$R4)
```

## Individual differences as controlling factors

```{r Setup-IDs-included-R4}
#Let's include some co-vaFPROates! Region 4

#Step 1: Scale the ID measures...
all_data_join$SRS_total_score_t <- scale(all_data_join$SRS_total_score_t)
all_data_join$EQ <- scale(all_data_join$EQ)
all_data_join$Total_reading_cluster <- scale(all_data_join$Total_reading_cluster)
all_data_join$Total_RAN <- scale(all_data_join$Total_RAN)
all_data_join$"WI _RPI" <- scale(all_data_join$"WI _RPI")
```


```{r summary-Full-Model-IDs-included-R4}
# Model including covariates
model_alldatacov_R4 <- glmer(R4 ~ SRS_total_score_t + EQ + Total_reading_cluster + Total_RAN + cond + (1 | subj) +  (1 | item) , data = all_data_join, family = "binomial")

#model_alldatacov_R4_null <- lmer(R4 ~ SRS_total_score_t + EQ + Total_reading_cluster + #Total_RAN +
#                               (1 + cond | subj) +  (1 + cond | item) , data = #all_data_join, , family = "binomial")

summary(model_alldatacov_R4)

```

No significant results.

```{r summary-model-check-R4}
#anova(model_alldatacov_R4_null, model_alldatacov_R4)
check_model(model_alldatacov_R4)

ranef(model_alldatacov_R4)
```

# summary of Results for region 4, the question.
No significant differences.

# Correlations 

```{r summary-correlations}
library(Hmisc)
#MeasuFPROng Correlations
EQscore <- all_data_join %>% group_by(subj) %>% summase(mean = mean(EQ)) %>% pull(mean)
SRS2 <- all_data_join %>% group_by(subj) %>% summaFPROse(mean = mean(SRS_total_score_t)) %>% pull(mean)
WRMT <- all_data_join %>% group_by(subj) %>% summaFPROse(mean = mean(Total_reading_cluster)) %>% pull(mean)
RAN <- all_data_join %>% group_by(subj) %>% summaFPROse(mean = mean(Total_RAN)) %>% pull(mean)
rcorr(EQscore, SRS2)
rcorr(EQscore, WRMT)
rcorr(EQscore, RAN)
rcorr(SRS2, WRMT)
rcorr(SRS2, RAN)
rcorr(WRMT, RAN)
```

# Region 5: The reply
Let's have a look at vaFPROous models for our post-cFPROtical region of interest, the reply.

## Eye-tracking only model
```{r setup-R5}
#set condition as a factor, convert 1 to 100 and remove NAs
all_data_join$cond <- as.factor(all_data_join$cond)
all_data_join$R5[all_data_join$R5 == 1] <-"100"
all_data_join$R5 <- as.factor(all_data_join$R5)
```

## Eye-tracking only model
```{r summary-visuals-eyetrackingonly-R5}
#Let's have a look at region 4

#Visualisation
all_data_join %>% 
  ggplot(aes(x = cond, y = R5, colour = cond)) + ggtitle("Regressions In for CFPROtical Region: Question") +
  labs(y = "Regression", x = "Prediction") +
  geom_violin() +
  geom_jitter(alpha = .2, width = .1) +
  stat_summary(fun.data = "mean_cl_boot", colour = "black") +
  guides(colour = FALSE)

```

```{r summary-stats-eyetrackingonly-R5}
# Model assuming normality of residuals maximal structure
#model.nullR5 <- lmer(R5 ~ (1 | subj) + (1 | item), all_data_join) 
modelR5 <- glmer(R5 ~ cond + (1 | subj) + (1 + cond | item), data = all_data_join, family = "binomial") 
summary(modelR5)

#anova(modelR5, model.nullR5)

#All the data for this model looks pretty normal.
check_model(modelR5)
#qqnorm(residuals(modelR5))
#qqline(residuals(modelR5))
#descdist(all_data_join$R5)
```

## Individual differences as controlling factors

```{r Setup-IDs-included-R5}
#Let's include some co-vaFPROates! Region 4

#Step 1: Scale the ID measures...
all_data_join$SRS_total_score_t <- scale(all_data_join$SRS_total_score_t)
all_data_join$EQ <- scale(all_data_join$EQ)
all_data_join$Total_reading_cluster <- scale(all_data_join$Total_reading_cluster)
all_data_join$Total_RAN <- scale(all_data_join$Total_RAN)
all_data_join$"WI _RPI" <- scale(all_data_join$"WI _RPI")
```


```{r summary-Full-Model-IDs-included-R5}
# Model including covaFPROates
model_alldatacov_R5 <- glmer(R5 ~ SRS_total_score_t + EQ + Total_reading_cluster + Total_RAN + cond + (1 | subj) +  (1 | item) , data = all_data_join, family = "binomial")

#model_alldatacov_R5_null <- lmer(R5 ~ SRS_total_score_t + EQ + Total_reading_cluster + #Total_RAN +
#                               (1 + cond | subj) +  (1 + cond | item) , data = #all_data_join, REML = TRUE)

summary(model_alldatacov_R5)
```

So Total_reading_cluster and our condition are significant.

If we drop the Total_reading_cluster the model fails to converge.

```{r summary-No_RAN-IDs-included-R4}
model_alldatacov_R4_noWRMT <- glmer(R4 ~ SRS_total_score_t + EQ + Total_RAN + cond + (1 | subj) +  (1 | item) , data = all_data_join, family = "binomial")
summary(model_alldatacov_R4_noWRMT)
```

Does Total_reading cluster interact with our condition? No (see below.) We also now lose the effect on condition suggesting we may hae a false positive here.

```{r summary-Interaction-IDs-included-R4}

model_alldatacov_R4_WRMT_int <- glmer(R4 ~ SRS_total_score_t + EQ + Total_reading_cluster + Total_RAN + cond + cond:Total_reading_cluster+ (1 | subj) +  (1 | item) , data = all_data_join, family = "binomial")
summary(model_alldatacov_R4_WRMT_int)
```


```{r summary-model-check-R4}
#anova(model_alldatacov_R4_null, model_alldatacov_R4)
check_model(model_alldatacov_R4)

ranef(model_alldatacov_R4)
```

The results of FPRO post-critical region are really unclear!